### 2014-12-03 Draft/background.tex
Dr. Xie's coments
Updated Introduction for flow Updated abstract with goal statement. Minor changes elsewhere.
compressive -> comprehensive added Software Engineering(SE)
Updated Draft for DSN
Updated Draft for DSN

In particular, this work proposes novel techniques on top of previously proposed techniques~\cite{pandita12:inferring, pandita13:WHYPER} to demonstrate the effectiveness of applying NLP on API documents.
We next briefly introduce the techniques used in this work that have been grouped into broad categories.
We first introduce the core NLP techniques used in this work.
We then introduce the SE specific NLP techniques proposed in previous work~\cite{pandita12:inferring,pandita13:WHYPER} that are used in this work.

@@

@@

\textbf{Noun Boosting}~\cite{pandita12:inferring}. Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
However, as mentioned previously, POS tagging works satisfactorily on well written news articles which does not necessary entail that the tagging works satisfactorily on domain specific text as well.
Thus, noun boosting is a necessary precursor to application of POS tagging on domain specific text.
In particular, with respect to API documents certain words have a different semantic meaning, in contrast to general linguistics that causes incorrect annotation of POS tags.

@@

\textbf{Lexical Token Reduction}~\cite{pandita13:WHYPER}.
These are a group of generic preprocessing heuristics to further improve the accuracy of core NLP techniques.
The accuracy of core NLP techniques is inversely proportional to the number of lexical tokens in a sentence.
Thus, the reduction in the number of lexical tokens greatly increases the accuracy of core NLP techniques. 
In particular, following heuristics have been used in previous work to achieve the desired reduction of lexical tokens:

@@

\textbf{Intermediate-Representation Generation}~\cite{pandita13:WHYPER}.
This technique accepts the syntax-annotated sentences and builds a First-Order-Logic(FOL) representation of the sentence.
Earlier researches have shown the adequacy using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring}.
In particular, WHYPER~\cite{pandita13:WHYPER} demonstrates the effectiveness of this technique, by constructing an intermediate representation generator based on shallow parsing~\cite{Branimir2000} techniques. 
The shallow parser itself is implemented as a sequence of cascading finite state machines based on the function of Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03}.

In next section we describe our proposed generic approach to infer constraints from API documents.

>>>>

%In particular, this work proposes novel techniques on top of previously proposed techniques~\cite{pandita12:inferring, pandita13:WHYPER} to demonstrate the effectiveness of applying NLP on API documents.
We next briefly introduce the techniques used in this work that have been grouped into broad categories.
We first introduce the core NLP techniques used in this work.
We then introduce the SE specific NLP techniques proposed in related work~\cite{pandita12:inferring,pandita13:WHYPER} that are used in this work.

@@

We next present Software Engineering (SE) specific NLP techniques.

@@

\textbf{Programming keywords}~\cite{pandita12:inferring}. Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
However POS tagging works satisfactorily on well-written news articles which does not necessary entail that the tagging works satisfactorily on domain-specific text as well.
Thus, noun boosting is a necessary precursor to application of POS tagging on domain specific text.
In particular, with respect to API documents certain words have a different semantic meaning, in contrast to general linguistics that causes incorrect annotation of POS tags.

@@

\textbf{Lexical Token Reduction}~\cite{pandita13:WHYPER}.
These are a group of generic preprocessing heuristics to further improve the accuracy of core NLP techniques.
The accuracy of core NLP techniques is often inversely proportional to the number of lexical tokens in a sentence.
Thus, the reduction in the number of lexical tokens greatly increases the accuracy of core NLP techniques. 
In particular, following heuristics have been used in previous work to achieve the desired reduction of lexical tokens:

@@

\textbf{Intermediate-Representation Generation}~\cite{pandita13:WHYPER}.
This technique accepts the syntax-annotated sentences (grammatical and semantic) and builds a First-Order-Logic (FOL) representation of the sentence.
Earlier researches have shown the adequacy using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring}.
In particular, WHYPER~\cite{pandita13:WHYPER} demonstrates the effectiveness of this technique, by constructing an intermediate representation generator based on shallow parsing~\cite{Branimir2000} techniques. 
The shallow parser itself is implemented as a sequence of cascading finite state machines based on the function of Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03}.

In next section we describe our generic approach to infer temporal constraints from API documents.

### 2014-12-03 Draft/conclusion.tex
Updated Draft for DSN
Updated Draft for DSN

Despite being highly desirable, most APIs are not equipped with formal temporal constraints.
In contrast, documentation of API methods contains detailed specifications of temporal constraints in natural language text.
Manually writing formal specifications based on natural language text in API documents is prohibitively time consuming and error prone.
To address this issue, we have proposed a novel approach called \tool\ to infer temporal constraints from natural language text of API documents.
We applied \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} in the JDK API and from the \amazonAPI.
Our evaluation results show that \tool\ effectively identifies sentences describing
temporal constraints with an average 65\% precision and 72\% recall,
from more than 3900 sentences in subject API documents.
Furthermore, \tool\ also achieved an accuracy of
70\% in inferring 63 formal temporal constraints from these sentences.

>>>>

Despite being highly desirable, most APIs are not equipped with formal temporal constraints.
In contrast, documentation of API methods contains detailed specifications of temporal constraints in natural language text.
Manually writing formal specifications based on natural language text in API documents is prohibitively time consuming and error prone.
To address this issue, we have proposed a novel approach called \tool\ to infer temporal constraints from natural language text of API documents.
We applied \tool\ to infer temporal constraints from
\paypalAPI, \amazonAPI, and  
commonly used package \CodeIn{java.io} in the JDK API.
Our evaluation results show that \tool\ effectively identifies sentences describing
temporal constraints with an average 65\% precision and 72\% recall,
from more than 4000 sentences in subject API documents.
Furthermore, \tool\ also achieved an accuracy of
70\% in inferring 63 formal temporal constraints from these sentences.

### 2014-12-03 Draft/evaluation.tex
Updated Draft for DSN
Updated Draft for DSN

We used the API documents of the following two libraries as subjects for our evaluation. 
\begin{itemize}
	\item \amazonAPI\: provides a REST based web services interface that can be used to store and retrieve data on the web. Furthermore, \CodeIn{Amazon S3} also empowers a developer with rich set of API methods to access a highly scalable, reliable, secure, fast, inexpensive infrastructure. \CodeIn{Amazon S3} is reported to store more than 2 trillion objects as of April 2013 and gets over 1.1 million requests per second at peak time~\cite{amazons3stats}.

	\item\CodeIn{java.io} : is one of a popular packages in \CodeIn{Java} programming language. The package provides APIs for system input and output through data streams, serialization and the file system, which are one of the fundamental functionalities provided by a programming language.
\end{itemize}
We chose \CodeIn{Amazon S3} and \CodeIn{java.io} APIs as our subjects because they are popular and contain decent documentation.

@@

\begin{tabular}{lcccccccccccc}
\topline
\headcol API & Mtds & Sen & Sen$_C$ & Sen$_{ICON}$ & TP & FP & FN & P(\%) & R(\%) & F$_S$(\%) & Spec$_{ICON}$ & Acc(\%)\\
\midline 
java.io & 662 & 2417 & 78 & 88 & 57 & 31 & 21 & 64.8 & 73.1 & 68.8 & 56 & 71.8\\ 
\rowcol AMAZON S3 REST & 51 & 1492 & 12 & 12 & 8 & 4 & 4 & 66.7 & 66.7 & 66.7 & 7 & 58.3\\ 
Total & 713 & 3909 & 90 & 100 & 65 & 35 & 25 & 65.0$^*$ & 72.2$^*$ & 68.4$^*$ & 63 & 70.0$^*$\\ 
\bottomlinec
%----------------- END TABLE DATA ------------------------ 
\multicolumn{13}{p{6.5in}}{\small
$^*$ Column average;
Mtds: Total no. of Methods; Sen: Total no. of Sentences; Sen$_C$: Total no. of constraint Sentences;
Sen$_{ICON}$: Total no. of constraint Sentences identified by \tool; 
TP: Total no. of True Positives; FP: Total no. of False Positives; FN: Total no. of False Negatives;
P: Precision; R: Recall; F$_S$: F-Score; Acc: Accuracy
Spec$_{ICON}$: Total no. of temporal constraint correctly identified by \tool;
} \\ 
\end{tabular}
\label{tab:results}
\end{center}
\end{table*}

>>>>

We used the API documents of the following two libraries as subjects for our evaluation. 
\begin{itemize}
	\item \amazonAPI\: provides a REST based web services interface to store and retrieve data on the web.
	Furthermore, \CodeIn{Amazon S3} also empowers a developer with rich set of API methods to access a highly scalable, reliable, secure, fast, and inexpensive infrastructure. 
	\CodeIn{Amazon S3} is reported to store more than 2 trillion objects as of April 2013 and gets over 1.1 million requests per second at peak time~\cite{amazons3stats}.

	\item \paypalAPI\: provides a REST based web service interface to facilitate online payments and money transfer.
	\CodeIn{PayPal} reports to have handled \$56.6 billion(USD) worth of transactions (total value of transactions) in just the third quarter of 2014.

	\item\CodeIn{java.io} : is one of a popular packages in \CodeIn{Java} programming language. The package provides APIs for system input and output through data streams, serialization and the file system, which are one of the fundamental functionalities provided by a programming language.
\end{itemize}
We chose \CodeIn{Amazon S3}, \CodeIn(PayPal) and \CodeIn{java.io} APIs as our subjects because they are popular and contain decent documentation.

@@

\begin{tabular}{lcccccccccccc}
\topline
\headcol API & Mtds & Sen & Sen$_C$ & Sen$_{ICON}$ & TP & FP & FN & P(\%) & R(\%) & F$_S$(\%) & Spec$_{ICON}$ & Acc(\%)\\
\midline 
java.io & 662 & 2417 & 78 & 88 & 57 & 31 & 21 & 64.8 & 73.1 & 68.8 & 56 & 71.8\\ 
\rowcol \amazonAPI & 51 & 1492 & 12 & 12 & 8 & 4 & 4 & 66.7 & 66.7 & 66.7 & 7 & 58.3\\ 
\paypalAPI & 33	&	151 &  20 &  &  &  &  & &  &  &  & \\ 
\rowcol Total & 746 & 4060 & 90 & 100 & 65 & 35 & 25 & 65.0$^*$ & 72.2$^*$ & 68.4$^*$ & 63 & 70.0$^*$\\ 
\bottomlinec
%----------------- END TABLE DATA ------------------------ 
\multicolumn{13}{p{6.5in}}{\small
$^*$ Column average;
Mtds: Total no. of Methods; Sen: Total no. of Sentences; Sen$_C$: Total no. of constraint Sentences;
Sen$_{ICON}$: Total no. of constraint Sentences identified by \tool; 
TP: Total no. of True Positives; FP: Total no. of False Positives; FN: Total no. of False Negatives;
P: Precision; R: Recall; F$_S$: F-Score; Acc: Accuracy
Spec$_{ICON}$: Total no. of temporal constraint correctly identified by \tool;
} \\ 
\end{tabular}
\label{tab:results}
\end{center}
\end{table*}

### 2014-12-03 Draft/example.tex
included formal def
Updated Draft for DSN
Updated Draft for DSN

We next present a real world example to motivate our approach.
In particular, through the example, we demonstrate that developers often ignore the temporal constraints of an API described in the documentation.
We suspect the reason for this phenomena is that the documentation is often verbose and the information is distributed across various pages.
For instance, the PDF version of the documentation for \amazonAPI\footnote{{\small \url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}}} spans 278 pages.
Developers often may not have time (and/or patience) to go through all the documentation and may overlook some temporal constraints of the API,
resulting in defective client applications that invoke API methods in sequences prohibited by documentation.

@@

Consider the question asked in \textit{Stack Overflow}~\footnote{{\small \url{http://stackoverflow.com/}}} as shown in Figure~\ref{fig:Stackoverflow}.
Stack Overflow is an online question and answer forum for professional and enthusiast programmers.
The query is about the delete functionality of a third-party software \CodeIn{S3Fox} to interact with \amazonAPI.
The inquisitor complains about an issue in the delete bucket functionality of the \CodeIn{S3Fox}.
The \CodeIn{S3Fox} developers overlooked the constraints in \amazon, causing the issue.
The API document pertaining to the  delete bucket functionality states that before deleting the bucket, the objects in the buckets must be deleted.
\textit{``All objects (including all objects versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted''}.
The issue was fixed.
However, one of the forum responses contained a recommendation for the inquisitor to switch to another product.
Customer dissatisfaction, such as was caused by this issue with the delete bucket functionality, can lead to a lose in revenue.

The preceding issue can be easily detected using formal analysis tools.
For instance, a specification rule (temporal constraint) can be added to a static checker to verify
the presence of a call to delete object functionality before the call to delete bucket functionality.
%However, existing formal analysis accept only formal specifications but not informal constraints described in natural language.
%Thus, there is need for an approach to automatically translate the constraints described in natural language into a more formal notation.
In next section, we briefly discuss the related work pertinent to our proposed approach.

>>>>

We next present a real world example to motivate our approach.
Through the example, we demonstrate that developers often ignore the temporal constraints of an API described in the documentation.
We suspect the reason for this phenomena is that the documentation is often verbose and the information is distributed across various pages.
For instance, the PDF version of the documentation for \amazonAPI\footnote{{\small \url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}}} spans 278 pages.
Often developers may not have time (and/or patience) to go through all the documentation and may overlook some temporal constraints of the API,
resulting in defective client applications that invoke API methods in sequences prohibited by documentation.

@@

Consider the question asked in \textit{Stack Overflow}~\footnote{{\small \url{http://stackoverflow.com/}}} as shown in Figure~\ref{fig:Stackoverflow}.
Stack Overflow is an online question and answer forum for professional and enthusiast programmers.
The query is about the delete functionality of a third-party software \CodeIn{S3Fox} to interact with \amazonAPI.
The inquisitor complains about an issue in the delete bucket functionality of the \CodeIn{S3Fox}.
The \CodeIn{S3Fox} developers overlooked the constraints in \amazon, causing the issue.
The API document pertaining to the  delete bucket functionality states that before deleting the bucket, the objects in the buckets must be deleted.
\textit{``All objects (including all objects versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted''}.
Although the issue was fixed, one of the forum responses contained a recommendation for the inquisitor to switch to another product.
Customer dissatisfaction, such as the one was caused by this issue with the delete bucket functionality, can lead to a loss in revenue.

The presented issue can be easily detected using formal analysis tools.
For instance, a specification rule (temporal constraint) can be added to a static checker to verify
the presence of a call to delete object functionality before the call to delete bucket functionality.
%However, existing formal analysis accept only formal specifications but not informal constraints described in natural language.
%Thus, there is need for an approach to automatically translate the constraints described in natural language into a more formal notation.
In next section, we briefly discuss the related work pertinent to our approach.

### 2014-12-03 Draft/formal.tex
Updated Draft for DSN
Updated Draft for DSN

\section{Temporal Specifications}
\label{sec:temporal}

In this section we describe various classes of temporal constraints using formal temporal logic.
In computer science, temporal Logic is a system of rules and symbols that are used to express and reason about prepositions pertaining to time.
We next present an extension to the temporal logic for API method invocation related rules proposed by Lo et al.~\cite{lo2009mining}

\textbf{Method Invocation}: 
We adapt the definition of events proposed by Lo et al.~\cite{lo2009mining} as method invocation.
They define event as \textit{``any concrete or abstract representation of a program state''}. 
We propose the notion of method invocation analogous to the events,
where each method invocation is represented as a tuple which is an ordered set of strings. 
A method invocation is captured as the Tuple <$T$><\CodeIn{str1, str2, str3}...>, where \CodeIn{str1, str2, str3}... are string values,
that belong to set of all strings.
The method invocation tuple <$T$> captures information about the return value, enclosing type, name, and the parameter types of the method.
Therefore a tuple <$T$><\CodeIn{String, Bar, foo, Integer, Integer}> represents a method \CodeIn{foo} enclosed by the type \CodeIn{Bar},
that accepts two parameters of type \CodeIn{Integer} and a return value of type \CodeIn{String}. 
For better readability mnemonic representation of the preceding tuple is \CodeIn{String<-Bar.foo(Integer, Integer);}

@@

\textbf{Temporal Operators}: Temporal formulae (temporal constraints) are constructed by combining method invocation predicates using temporal operators. Lo et al.~\cite{lo2009mining}, proposed the following temporal operators

@@

We extend these operators by proposing two additional operators:
\begin{enumerate}
\item Forward Prohibition Operator ($\xi_1 \nrightarrow \xi_2$):
occurrence of $\xi_1$ cannot be followed by occurrence of $\xi_2$

\item Backward Prohibition Operator ($\xi_1 \nleftarrow \xi_2$):
occurrence of $\xi_1$ cannot be preceded by the occurrence of $\xi_2$
\end{enumerate}

The prohibition operators capture a different class of temporal constraints that cannot be expressed by the formulae constructed by previously proposed operators and their negations. For instance, the \textit{prohibition operators} on first glance seem to be negation of \textit{forward eventual operators} and \textit{backward eventual operators}. However, the negation of forward eventual operators is: not an invocation of e1 must be eventually followed by not an invocation of m2. In contrast, \textit{prohibition operators} either negates antecedent or consequent but not both.

\textbf{Quantification}: Quantification is used to introduce constraints involving parameter and return types of a method invocation. For instance, consider the constraint any method in an enclosing type \CodeIn{Obj} must not be invoked after method \CodeIn{foo} in the \CodeIn{Obj}.

$\forall$ \CodeIn{m <m in Obj> !=<foo in Obj>}

In summary, we extended the formalism for temporal rules previously proposed by Lo et al.~\cite{lo2009mining} to express temporal constraints.
We obtain different classes of temporal constraints by varying: 1) the temporal operators allowed, b) the method-invocation predicates allowed, and 3) the degree of quantification allowed.

>>>>

\subsection{Temporal Specifications}
\label{sub:temporal}

We next describe various classes of temporal constraints using formal temporal logic.
Temporal logic is a system of rules and symbols that are used to express and reason about prepositions pertaining to time.
We next present an extension to the temporal logic for API method invocation related rules proposed by Lo et al.~\cite{lo2009mining}

\textbf{Method Invocation}: 
We adapt the definition of events proposed by Lo et al.~\cite{lo2009mining} as method invocation.
They define event as \textit{``any concrete or abstract representation of a program state''}. 
We propose the notion of method invocation analogous to the events,
where each method invocation is represented as a tuple which is an ordered set of strings. 
A method invocation is captured as the Tuple \CodeIn{<T> <str1, str2, str3... >}, where \CodeIn{str1, str2, str3}... are string values,
that belong to set of all strings.
The method invocation tuple \CodeIn{<T>} captures information about the return value, enclosing type, name, and the parameter types of the method.
Therefore a tuple \CodeIn{<T> <String, Bar, foo, Integer, Integer>} represents a method \CodeIn{foo} enclosed by the type \CodeIn{Bar},
that accepts two parameters of type \CodeIn{Integer} and a return value of type \CodeIn{String}. 
For better readability mnemonic representation of the preceding tuple is \CodeIn{String<-Bar.foo(Integer, Integer);}

@@

\textbf{Temporal Operators}: Temporal constraints~\footnote{Temporal formulae} are constructed by combining method invocation predicates using temporal operators. Lo et al.~\cite{lo2009mining}, proposed the following temporal operators:

@@

\textbf{Quantification}: Quantification is used to introduce constraints involving parameter and return types of a method invocation. Formal representation of temporal constraints are obtained by varying: 1) the temporal operators allowed, b) the method-invocation predicates allowed, and 3) the degree of quantification allowed. For instance, consider the constraint any method in an enclosing type \CodeIn{Obj} must not be invoked after method \CodeIn{foo} in the \CodeIn{Obj}: $\forall$ \CodeIn{m <m in Obj> !=<foo in Obj>}.

### 2014-12-03 Draft/introduction.tex
Updated Draft for DSN
Updated Draft for DSN

The increasing reach of internet has fueled the growth of web Application Programming Interfaces (API).
The ProgrammableWeb reports that the web APIs have doubled from Jan 2012 to Oct 2013\footnote{\url{http://www.programmableweb.com/api-research}}.
These APIs are being combined in interesting ways by application developers creating third-party applications using
these APIs to provide value added service.
For instance, many online stores leverage Paypal API to assist users with paying for the purchased commodities without actually
providing financial information to the online store.

Unlike most traditional API libraries that are in the format of locally stored binary files and are programming language specific,
web API are designed to leverage the web server and web browser architecture and the implementation is programming language agnostic.
However, Web APIs like traditional APIs have rules or constraints governing the proper  use of the API that must be followed.
One such type of constraints are temporal constraints [2], which are the allowed sequences of invocations of methods from the API.
Non-compliance to such constraints can result in faulty applications that are unreliable to use and may even result in financial losses.

In traditional API, which are usually implemented in typed languages some temporal constraints are enforced by type system itself.
For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates
that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
Thus compliance of such constraints are easily enforced by compilers.
In contrast to traditional API libraries, web APIs work on basic parameter data types such as \CodeIn{strings} and \CodeIn{numbers}.
Therefore enforcing temporal constraints through type system is ineffective in web APIs.
Additionally temporal constraints are not entirely restricted to type definitions.

@@

Although natural language API description can be manually converted into formal constraints,
manually writing formal constraints based on natural language text in API documents can be prohibitively time consuming and error prone~\cite{wu2013inferring,RubingerWEB10}. 
For instance, Wu et al.~\cite{wu2013inferring} report that it took one person ten hours to browse the documentation of one method from a web service API, even before the person attempted to formalize the constraints on the method.

To reduce the manual effort, we propose \tool: a Natural Language Processing (NLP) based approach
to automatically infer formal temporal constraints. 
However, inferring temporal constraints from the natural language text is challenging. 
In particular, our approach addresses two major challenges to automatically infer specifications
from natural language text in API documents.

First, existing NLP techniques are initially designed towards well-written news articles.
In contrast, API documents are domain-specific documents and are often not well formed.
Furthermore, we observe that generic NLP techniques face problems with lengthy sentences (with a number of lexical tokens).
Consider the description sentence ``All objects (including all object versions and Delete Markers) in the bucket must be deleted before the bucket itself can be delete.'' The length of the sentence may overwhelm an NLP parser, which then inaccurately extracts semantic relations between the words in the sentence.
Our ICON approach includes a new technique called ``hybrid parsing'' to deal with the number of lexical tokens.
Hybrid parsing automatically breaks lengthy sentences to smaller tractable sentences based on a function of parts-of-speech tags.

Second, after API documents are made amenable to existing NLP techniques, a method referenced in the natural language text must be identified in order to infer temporal constraints on the method but such method referencing is often implicit.
Consider the description sentence ``You must initiate a multipart upload before you can upload any part.''
In this sentence, phrases ``multipart upload'' and ``upload any part'' refer to individual methods in the API.
Identifying these phrases as method-invocation instances requires domain dictionaries.
Ad-hoc construction of such dictionaries is prohibitively resource intensive and error-prone.
To address this challenge, we propose to build domain dictionaries systematically from API documents and generic English dictionaries.

@@

\begin{itemize}
	\item An NLP-based approach that effectively infers temporal constraints of method invocations. 
	To the best of our knowledge, our approach is the first one to apply NLP for inferring temporal constraints from API documents.
	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03}, which is a natural language parser to derive the grammatical structure of sentences.
	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}, along with the experimental subjects and the results. 
	\item An evaluation of our approach on \amazonAPI, \paypalAPI, and commonly used package \CodeIn{java.io} from the JDK API. 
\end{itemize}

The rest of the paper is organized as follows.
Section~\ref{sec:example} presents a real-world example that motivates our approach.
Section~\ref{sec:related} discusses related work.
Section~\ref{sec:background} presents the  background on NLP techniques used in our approach.
Section~\ref{sec:approach} presents our approach.
Section~\ref{sec:evaluation} presents the evaluation of our approach.
Section~\ref{sec:discussion} presents brief discussion and future work.
Finally, Section~\ref{sec:conclusion} concludes.

>>>>

The increasing reach of the internet has fueled the growth of web Application Programming Interfaces (API).
The ProgrammableWeb reports that the web APIs have doubled from Jan 2012 to Oct 2013\footnote{\url{http://www.programmableweb.com/api-research}}.
These APIs are being combined in interesting ways by application developers creating third-party applications using
these APIs to provide value added service.
For instance, many online stores leverage Paypal API to assist users with paying for the purchased commodities without actually
providing financial information to the online store.

Unlike most traditional API libraries that are in the format of locally stored binary files and are programming language specific,
web APIs are designed to leverage the web server and web browser architecture and the implementation is programming language agnostic.
However, Web APIs like traditional APIs have rules or constraints governing the proper  use of the API that must be followed.
One such type of constraints are temporal constraints [2], which are the allowed sequences of invocations of methods from the API.
Non-compliance to such constraints can result in faulty applications that are unreliable to use and may even result in financial losses.

In traditional API, which are usually implemented in typed languages some temporal constraints are enforced by the type system itself.
For instance, a method ($m$) accepting input parameter ($i$) of type ($t$) mandates
that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
Thus compliance of such constraints are easily enforced by compilers.
In contrast to traditional API libraries, web APIs work on basic parameter data types such as \CodeIn{strings} and \CodeIn{numbers}.
Therefore enforcing temporal constraints through type system is ineffective in web APIs.
Additionally, temporal constraints are not entirely restricted to type definitions.

@@

Although natural language API description can be manually converted into formal constraints,
manually writing formal constraints based on natural language text in API documents can be prohibitively time consuming and error prone~\cite{wu2013inferring,RubingerWEB10}. 
For instance, Wu et al.~\cite{wu2013inferring} report that it took one person ten hours to browse the documentation of one method from a web API, even before the person attempted to formalize the constraints on the method.

To reduce the manual effort, we propose \tool: a Natural Language Processing (NLP) based approach
to automatically infer formal temporal constraints. 
In particular, our approach addresses two major challenges to automatically infer specifications
from natural language text in API documents.

First, existing NLP techniques are initially designed towards well-written generic news articles.
In contrast, API documents are domain-specific documents and are often not well formed.
Furthermore, we observe that generic NLP techniques face problems with lengthy sentences (with a number of lexical tokens).
Consider the description sentence ``All objects (including all object versions and Delete Markers) in the bucket must be deleted before the bucket itself can be delete.'' The length of the sentence may overwhelm an NLP parser, which then inaccurately extracts semantic relations between the words in the sentence.
Our ICON approach includes a new technique called ``hybrid parsing'' to deal with the number of lexical tokens.
Hybrid parsing automatically breaks lengthy sentences to smaller tractable sentences based on a function of parts-of-speech tags.

Second, after API documents are made amenable to existing NLP techniques, a method referenced in the natural language text must be identified to infer temporal constraints on the method but such method referencing is often implicit.
Consider the description sentence ``You must initiate a multipart upload before you can upload any part.''
In this sentence, phrases ``multipart upload'' and ``upload any part'' refer to individual methods in the API.
Identifying these phrases as method-invocation instances requires domain dictionaries.
Ad-hoc construction of such dictionaries is prohibitively resource intensive and error-prone.
To address this challenge, we propose to build domain dictionaries systematically from API documents and generic English dictionaries.

@@

\begin{itemize}
	\item An NLP-based approach that effectively infers formal temporal constraints of method invocations. 
	To the best of our knowledge, our approach is the first one to apply NLP for inferring temporal constraints from API documents.
	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03}, which is a natural language parser to derive the grammatical structure of sentences.
	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}, along with the experimental subjects and the results. 
	\item An evaluation of our approach on \amazonAPI, \paypalAPI, and commonly used package \CodeIn{java.io} from the JDK API. 
\end{itemize}

The rest of the paper is organized as follows.
Section~\ref{sec:example} presents a real-world example that motivates our approach.
Section~\ref{sec:related} discusses related work.
Section~\ref{sec:background} presents the  background on NLP techniques used in our approach.
Section~\ref{sec:approach} presents our approach.
Section~\ref{sec:evaluation} presents the evaluation of our approach.
Section~\ref{sec:discussion} presents brief discussion on the limitations and future work.
Finally, Section~\ref{sec:conclusion} concludes.
